Spin canonical divisors of log stacky curves

### 2015-06-23 stacky_write_up/spin_cring.tex
additions to corollaries of induction when saturated at 1

\begin{cor}\label{cor:genus_0_posiive_delta}
Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
\end{cor}
\begin{proof}
Since $\halfcan$ is a half canonical divisor, 
\[
	2\halfcan=D+\sum \subhalf{i}P_i
\] 
where 
\[
	D\sim K_X+\Delta\sim -2\infty+ \Delta
\] is a divisor of $X$ (i.e. with 
possibly negative integer coefficients).  Since $\Delta$ is non-
zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
any point $P$ occurring in a stacky divisor of $\sx$ must have 
coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
s appearing in the characteristic of $(\sx,\Delta)$).

>>>>

\begin{cor}\label{cor:genus_0_posiive_delta}
Let $\halfcan$ be a stacky log spin canonical divisor of $(X,\Delta)$ with signature $(g;e_1,\ldots, e_n;\delta)$ such that $2\halfcan=K_\sx+\Delta$ with $\delta=\deg(\Delta)>0$.  Then $\halfcan$ is effective so we can inductively apply lemma \ref{lem:deg1_sat_ind}.
\end{cor}
\begin{proof}
Since $\halfcan$ is a half canonical divisor, 
\[
	2\halfcan=D+\sum \subhalf{e_i}P_i
\] 
where 
\[
	D\sim K_X+\Delta\sim -2\infty+ \Delta
\] is a divisor of $X$ (i.e. with 
possibly negative integer coefficients).  Since $\Delta$ is non-
zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
any point $P$ occurring in a stacky divisor of $\sx$ must have 
coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
s appearing in the characteristic of $(\sx,\Delta)$).
